---
bio: Equality & Justice.
education:
  courses:
  - course: PhD in Ecology & Evolution
    institution: Rio de Janeiro State University -  Brazil
    year: 2021
  - course: MsC in Ecology & Evolution
    institution: Rio de Janeiro State University  -  Brazil
    year: 2016
  - course: BSc in Biological Sciences
    institution: Universidade Federal do Espírito Santo -  Brazil
    year: 2008
email: ssantos.gabriel@gmail.com
highlight_name: false
interests:
- Demography
- Population modelling
- Applied statistics
- Invasive species
- Natural history
- Citizen science

organizations:
- name: Rio de Janeiro State University -  Brazil
  url: null
role: PhD Candidate
social:
- icon: envelope
  icon_pack: fas
  link: "mailto:ssantos.gabriel@gmail.com"
- display:
    header: false
  icon: twitter
  icon_pack: fab
  label: Follow me on Twitter
  link: https://twitter.com/anycommonname
- icon: graduation-cap
  icon_pack: fas
  link: https://scholar.google.com/citations?user=DXeK9HwAAAAJ&hl=en
- icon: lattes
  icon_pack: ai
  link: http://lattes.cnpq.br/1714610835853424
- icon: github
  icon_pack: fab
  link: https://github.com/ecosantos
superuser: true
title: Gabriel Santos
---

{{% callout note %}}
I'm migrating my [wixsite](https://gabeco.wixsite.com/home) to the Netlify using Rstudio & Blogdown & Hugo. Be tuned. 
{{% /callout %}}

I am a Brazilian population ecologist interested in many things, but particularly keen to explore the demographic drivers and fates of wildlife populations. I'm also an enthusiast of old school naturalists, citizen science and programming. 

Up to that, I'm a coffee seeker (*a.k.a* coffee addiction <i class="fas fa-coffee"></i>), beer taster, and an MPB (Brazilian Popular Music) lover.  Something in common? Be in touch! 

See you soon and take care :mask:



                                      Last time updated: `r Sys.Date()`

```{r echo=FALSE}
#Criei esse chunk para desaparecer com essa parte aqui por enquanto já que isso não funciona no formato .Rmd mas quero continuar usando essa ideia para deixar meu currículo disponív
#{{% callout note %}}
#{{< icon name="download" pack="fas" >}} Download my {{< staticref "./Resume/Resume.pdf" "newtab" >}}resumé{{< /staticref >}}.
#{{% /callout %}}
```


```{r echo=FALSE}

#Depois substitutir Sys.time() por Sys.Date
#                                      Last time updated: `r Sys.time()`
```

